---
title: "Tumour Genomic Research Report"
author: "Cris Print"
output: html_document
---

<link rel="stylesheet" type="text/css" href="http://cdn.datatables.net/1.10.5/css/jquery.dataTables.min.css">
<script src="http://code.jquery.com/jquery-2.1.2.min.js"></script>
<script src="http://cdn.datatables.net/1.10.5/js/jquery.dataTables.min.js"></script>

<script type="text/javascript">
         $(document).ready(function() {
             $(".dtable").DataTable();
         } );
</script>

```{r setup, include=FALSE}
opts_chunk$set(dev = 'pdf')
```

```{r, echo=FALSE}
suppressWarnings(suppressPackageStartupMessages(library(knitr)))
suppressWarnings(suppressPackageStartupMessages(library(markdown)))
suppressWarnings(suppressPackageStartupMessages(library(rmarkdown)))
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
suppressWarnings(suppressPackageStartupMessages(library(kableExtra)))
```

# `r Text1a`

<br>

### `r Text1b`

<br><br>

------

## Somatic Variants that pass filtering
<br>
`r 
if(is.vector(S.filtered.table)){
S.filtered.table} else {
S.filtered.table %>% mutate(Gene=paste0("<a href='https://www.genecards.org/cgi-bin/carddisp.pl?gene=",Gene,"'>",Gene,"</a>")) %>% mutate(IGV=paste0("<a href='http://localhost:60151/goto?locus=",IGV,"'>",IGV,"</a>")) %>%
    knitr::kable("html", table.attr = "class='dtable'", escape=F) %>% kable_styling(bootstrap_options = "striped")
}
`
<br>
`r Text0`
<br><br>

------


<br><br>

## Autosomal aneuploidy graphs (B-allele ferequency)
<br>
```{r, echo=FALSE, out.width = "900px", out.height= "350px"}
knitr::include_graphics(TT.image)
```

------

<br><br>

## Germline Variants that pass filtering
### (low stringency filters used. Only genes on clinician-supplied lists included)
<br>
`r 
if(is.vector(G.filtered.table)){
G.filtered.table} else {
G.filtered.table %>% mutate(ToIGV=paste0("<a href='http://localhost:60151/goto?locus=",ToIGV,"'>",ToIGV,"</a>")) %>% mutate(Gene=paste0("<a href='https://www.genecards.org/cgi-bin/carddisp.pl?gene=",Gene,"'>",Gene,"</a>")) %>% mutate(dbSNP147=paste0("<a href='https://www.ncbi.nlm.nih.gov/snp/",dbSNP147,"'>",dbSNP147,"</a>")) %>% knitr::kable("html", table.attr = "class='dtable'", escape=F) %>% kable_styling(bootstrap_options = "striped")
}
`
<br>

------


## Cancer Genome Interpreter recommendations related in any way to Somatic Variants that pass filtering (from late trials and guidelines only, amplification, fusion, overexpression and deletion are excluded).
<br>
`r 
if(is.vector(SCGId.table)){
SCGId.table} else {
knitr::kable(SCGId.table[,3:6]) %>% kable_styling(bootstrap_options = "striped")
}
`
<br><br>


### Somatic filters used
`r 
SomRulesText2
`

<br>

`r 
knitr::kable(SomRulesText1)
`

### Germline filters used
`r 
GLRulesText2
`

<br>

`r 
knitr::kable(GLRulesText1)
`
<br>

#### Not for clinical use. Analysis calibrated for research.


